Predicting Game of the Year (GOTY) 2024: A Bayesian Analysis of Video Game Metrics from Metacritic

### 2024-11-29 paper/paper.qmd
update paper, graph and scripts

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

bayesian_model <-
  readRDS(file = here::here("models/bayesian_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| warning: false
set.seed(617)
predicted_probs <- posterior_predict(bayesian_model, newdata = data_2024, type = "response")

data_2024$mean_prob <- apply(predicted_probs, 2, mean)

top_10_percent_threshold <- quantile(data_2024$mean_prob, 0.9)

data_2024 <- data_2024 %>%
  mutate(goty_status = ifelse(mean_prob >= top_10_percent_threshold, 1, 0))
```

@@

@@

# Count for genre of potential winners 
winner_2024 <- data_2024 %>%
  filter(mean_prob > 0)

@@

data_2024 %>%
  filter(goty_status == 1) %>%
  select(-user_positivity, -critic_positivity, -release_date, -goty_status) %>%
  rename(
    Genre = genre,
    "User Score" = user_score,
    "Score" = score
  ) %>%
  arrange(desc(mean_prob)) %>%
  mutate(Rank = row_number()) %>%
  relocate(Rank) %>% 
  kable(caption = "Potential winner of 2024 GOTY") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"), font_size = 6) %>%
  row_spec(0, bold = TRUE)
```

@@

## Model summary
```{r}
#| label: fig-model-result-ci
#| fig-cap: The credible intervals for coefficient estimates of predictors of a game wins GOTY
#| echo: false
#| warning: false
#| message: false

# Specify credible interval to be 90% and present model results
# modelplot(bayesian_model, conf_level = 0.9) +
#   labs(x = "90 per cent credible interval")
```

@@

Trace plot @fig-trace shows generally overlapping chains and @fig-rhat also shows values close to 1.0 for all parameters indicate good convergence. I didn't conduct residual vs. fitted and VUC checks because of the class imbalance of dataset.

>>>>

@@

prediction_2024 <- read_csv(here::here("data/03-prediction/prediction.csv"))

@@

# Count for genre of potential winners 
winner_2024 <- prediction_2024 %>%
  filter(mean_prob > 0)

@@

prediction_2024 %>%
  filter(goty_status == 1) %>%
  select(-user_positivity, -critic_positivity, -release_date, -goty_status) %>%
  arrange(desc(mean_prob)) %>%
  rename(
    Genre = genre,
    "User Score" = user_score,
    "Score" = score,
    "Predictit prob" = mean_prob
  ) %>%
  mutate(Rank = row_number()) %>%
  relocate(Rank) %>% 
  kable(caption = "Potential winner of 2024 GOTY") %>%
  kable_styling(full_width = FALSE, bootstrap_options = c("striped", "hover"), font_size = 6) %>%
  row_spec(0, bold = TRUE)
```

@@

@@

Trace plot @fig-trace shows generally overlapping chains and @fig-rhat also shows values close to 1.0 for all parameters indicate good convergence. I didn't apply residual vs. fitted and AUC checks because of the class imbalance of dataset.
